\addcontentsline{toc}{chapter}{Bibliografía}
\begin{thebibliography}{99}

\bibitem{reactnative} Meta Platforms, Inc. \emph{React Native. A framework for building native apps using React}. \url{https://reactnative.dev}

\bibitem{expo} Expo. \emph{Expo Documentation}. \url{https://docs.expo.dev}

\bibitem{reactquery} TanStack. \emph{TanStack Query (React Query)}. \url{https://tanstack.com/query}

\bibitem{springboot} Broadcom (VMware Tanzu). \emph{Spring Boot Reference Documentation}. \url{https://spring.io/projects/spring-boot}

\bibitem{springsecurity} Broadcom (VMware Tanzu). \emph{Spring Security Reference Documentation}. \url{https://spring.io/projects/spring-security}

\bibitem{openapi} OpenAPI Initiative. \emph{OpenAPI Specification}. \url{https://spec.openapis.org}

\bibitem{postgresql} The PostgreSQL Global Development Group. \emph{PostgreSQL Documentation}. \url{https://www.postgresql.org/docs/}

\bibitem{rfc7519} M. Jones, J. Bradley e N. Sakimura. \emph{JSON Web Token (JWT)}. RFC~7519, IETF, 2015. \url{https://www.rfc-editor.org/rfc/rfc7519}

\bibitem{rfc7807} M. Nottingham e E. Wilde. \emph{Problem Details for HTTP APIs}. RFC~7807, IETF, 2016. \url{https://www.rfc-editor.org/rfc/rfc7807}

\bibitem{ollama} Ollama. \emph{Ollama. Get up and running with large language models locally}. \url{https://ollama.com}

\bibitem{minio} MinIO, Inc. \emph{MinIO Object Storage Documentation}. \url{https://min.io}

\bibitem{bcrypt} N. Provos e D. Mazières. \emph{A Future-Adaptable Password Scheme}. Proceedings of the USENIX Annual Technical Conference, 1999.

\bibitem{podman} Red Hat, Inc. \emph{Podman. A tool for managing OCI containers and pods}. \url{https://podman.io}

\bibitem{testcontainers} AtomicJar / Docker, Inc. \emph{Testcontainers for Java}. \url{https://java.testcontainers.org}

\bibitem{jacoco} \emph{JaCoCo Java Code Coverage Library}. \url{https://www.jacoco.org/jacoco/}

\bibitem{nielsen1994usability} J. Nielsen. \emph{Usability Engineering}. Morgan Kaufmann, 1994.

\bibitem{tricount} Tricount (Bunq). \emph{Tricount. Split group expenses}. \url{https://www.tricount.com}

\bibitem{whatsapp} WhatsApp LLC. \emph{WhatsApp Messenger}. \url{https://www.whatsapp.com}

\bibitem{googlecalendar} Google LLC. \emph{Google Calendar}. \url{https://calendar.google.com}

\bibitem{wanderlog} Wanderlog. \emph{Wanderlog. Travel itinerary and trip planner}. \url{https://wanderlog.com}

\bibitem{travelperk} TravelPerk. \emph{TravelPerk. Business travel management}. \url{https://www.travelperk.com}

\end{thebibliography}
